Methods paper for erosion

### 2017-08-28 docs/methods/erosion_methods.tex
changed pores to bodies in methods paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Formulation\label{s:formulation}} 
We consider multiple bodies being eroded by a two-dimensional Stokesian
fluid.  The Stokes paradox is circumvented by using a rounded-off
rectangle that encloses the eroding bodies.  Then, the flow is driven
by a boundary conditions, such as a Hagen-Poiseuille flow, on the
boundary of the outer geometry \todo[inline]{Need a figure here}
\begin{subequations}
\label{eqn:erosionModel}
\begin{gather}
eqn1 \label{eqn:eqn1} \\
eqn2 \label{eqn:eqn2} \\
\pderiv{\xx}{\nn} = -|\tau| \label{eqn:poreEvolution}
\end{gather}
\end{subequations}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Computing the Shear Stress, Pressure, and Drag} 
The governing equations~\eqref{eqn:erosionModel} require the shear
stress which is defined on the boundary of each pore.  The shear stress
is given by
\begin{align}
  \tau = \left(\nabla \uu + \nabla \uu^T \right)\nn \cdot \ss,
  \label{eqn:shearStress}
\end{align}
where $\ss$ is the unit tangent vector.  We note that for the Stokes
equations, because of the no-slip boundary condition on the pores, the
shear stress is identical to the surface vorticity $\tau = u_y - v_x$.
However, we use equation~\eqref{eqn:shearStress} to compute the shear
stress since the jump conditions resulting from the double-layer
potential are known~\cite{qua-bir2014a}.  The velocity field of the
completed double-layer potential involves three terms: the double-layer
potential $\DD$, the Stokeslets $S$, and the rotlets $R$.  To compute
the shear stress, we first compute the deformation tensor $\ssigma =
\frac{1}{2}(\nabla\uu + \nabla\uu^T)$ of each of these terms
individually.

@@

Finally, with the pressure and shear stress, the drag on a single pore
with boundary $\Gamma_k$ is
\begin{align}
  F_D = \int_{\Gamma_k} (-p \nn + \tau \ss)\,ds.
\end{align}

@@

Once the shear stress is computed, it is used to update the shape of the
pores according to the normal flow~\eqref{eqn:poreEvolution}.  To
eliminate tangling and stretching of the mesh, we use a \thL
formulation~\cite{hou-low-she1994} which is described in
Section~\ref{sec:thetaL}.  In this section, we also describe our time
stepping method and two regularization terms that are necessary to
control the curvature of the pores and to maintain spectral accuracy in
space.

@@

We use a quasi-static approximation so that the velocity field
instantaneously changes with the changing geometry.  Therefore, we can
alternate between the two main aspects of our simulation
\begin{enumerate}
  \item Given a geometry, compute the shear stress of along each of the
  pores.
  \item Given the shear stress, update the geometry according to the
  erosion model.
\end{enumerate}

@@

In order to regularize boundary evolution, we modify Eq.~(\ref{eqn:poreEvolution}) to include a curvature-driven component (also corrected errors in this equation)
\begin{equation}
\pderiv{\xx}{t} = |\tau| \nn + \eps \elfun(L) \left(\kappa - \frac{2 \pi}{L} \right)
\end{equation}
The curvature term acts to smooth bodies that have high-frequency oscillations.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Formulation\label{s:formulation}} 
We consider multiple bodies being eroded by a two-dimensional Stokesian
fluid.  The Stokes paradox is circumvented by using a rounded-off
rectangle that encloses the eroding bodies.  Then, the flow is driven
by a boundary conditions, such as a Hagen-Poiseuille flow, on the
boundary of the outer geometry \todo[inline]{Need a figure here}
\begin{subequations}
\label{eqn:erosionModel}
\begin{gather}
eqn1 \label{eqn:eqn1} \\
eqn2 \label{eqn:eqn2} \\
\pderiv{\xx}{\nn} = -|\tau| \label{eqn:bodyEvolution}
\end{gather}
\end{subequations}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Computing the Shear Stress, Pressure, and Drag} 
The governing equations~\eqref{eqn:erosionModel} require the shear
stress which is defined on the boundary of each body.  The shear stress
is given by
\begin{align}
  \tau = \left(\nabla \uu + \nabla \uu^T \right)\nn \cdot \ss,
  \label{eqn:shearStress}
\end{align}
where $\ss$ is the unit tangent vector.  We note that for the Stokes
equations, because of the no-slip boundary condition on the bodies, the
shear stress is identical to the surface vorticity $\tau = u_y - v_x$.
However, we use equation~\eqref{eqn:shearStress} to compute the shear
stress since the jump conditions resulting from the double-layer
potential are known~\cite{qua-bir2014a}.  The velocity field of the
completed double-layer potential involves three terms: the double-layer
potential $\DD$, the Stokeslets $S$, and the rotlets $R$.  To compute
the shear stress, we first compute the deformation tensor $\ssigma =
\frac{1}{2}(\nabla\uu + \nabla\uu^T)$ of each of these terms
individually.

@@

Finally, with the pressure and shear stress, the drag on a single body
with boundary $\Gamma_k$ is
\begin{align}
  F_D = \int_{\Gamma_k} (-p \nn + \tau \ss)\,ds.
\end{align}

@@

Once the shear stress is computed, it is used to update the shape of the
bodies according to the normal flow~\eqref{eqn:bodyEvolution}.  To
eliminate tangling and stretching of the mesh, we use a \thL
formulation~\cite{hou-low-she1994} which is described in
Section~\ref{sec:thetaL}.  In this section, we also describe our time
stepping method and two regularization terms that are necessary to
control the curvature of the bodies and to maintain spectral accuracy in
space.

@@

We use a quasi-static approximation so that the velocity field
instantaneously changes with the changing geometry.  Therefore, we can
alternate between the two main aspects of our simulation
\begin{enumerate}
  \item Given a geometry, compute the shear stress of along the boundary
    of each of the bodies.
  \item Given the shear stress, update the geometry according to the
    erosion model.
\end{enumerate}

@@

In order to regularize boundary evolution, we modify
Eq.~(\ref{eqn:bodyEvolution}) to include a curvature-driven component
(also corrected errors in this equation)
\begin{equation}
\pderiv{\xx}{t} = |\tau| \nn + \eps \elfun(L) \left(\kappa - \frac{2 \pi}{L} \right)
\end{equation}
The curvature term acts to smooth bodies that have high-frequency oscillations.
